The Forecast Trap

### 2021-09-17 manuscript/manuscript.Rmd
abstract < 150 words

- abbreviated running title: "The Forecast Trap"
- Authorship statement: _This is a single-author paper_
- data accessibility statement: _All simulation data generated for analyses here, along with code required for the analysis, is available in the Zenodo Data archive, https://doi.org/10.5281/zenodo.4660621_
- number of words in the abstract: 172
- number of words in main text: 4967
- number of cited references: 33
- number of tables & figures: 4 Figures

>>>>

- abbreviated running title: "The Forecast Trap"
- Authorship statement: _This is a single-author paper_
- data accessibility statement: _All simulation data generated for analyses here, along with code required for the analysis, is available in the Zenodo Data archive, https://doi.org/10.5281/zenodo.4660621_
- number of words in the abstract: 149
- number of words in main text: 4967
- number of cited references: 33
- number of tables & figures: 4 Figures
